Turbulence in compact to giant HII regions

### 2022-05-18 strucfunc_paper.tex
Improve strucfunc figure captions

\begin{figure*}
  \centering
  \sffigggg{OrionS}{OrionLH}{M8}{CarC}
  \caption{
    Second-order structure functions
    for velocity centroid images
    of the \ha{} emission line
    from Galactic \hii{} regions.
    Blue symbols show the observed mean structure function
    in each radial bin.
  }
  \label{fig:strucfunc-fit-Galactic}
\end{figure*}

@@

\begin{figure*}
  \centering
  \sffigg{Dor}{N346}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-Galactic}
    except for Magellanic Cloud \hii{} regions. 
  }
  \label{fig:strucfunc-fit-MC}
\end{figure*}

\begin{figure*}
  \centering
  \sffigggg{HV}{HX}{N595}{N604H}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-Galactic}
    except for \hii{} regions in more distant
    Local Group Galaxies.
  }
  \label{fig:strucfunc-fit-ExtraGal}
\end{figure*}

@@

In order to provide a uniform description of the velocity fluctuations,
we fit the model structure function
\(\tilde{B}\mod(r)\) of equation~\eqref{eq:sf-functional}
to each \hii{} region in our sample.
Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
and~\ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
Best-fit values for the model parameters,
together with 95\% credibility range,
are given in Table~\ref{tab:Res}.
After describing the methods used to
measure the structure function and fit the model (section~\ref{sec:techn-deta-model}),
we give details of the results in the example case of
the inner Orion Nebula (\ref{sec:example-results-orion})
and a broad overview of the results for other regions (\ref{sec:results-model-fitt}).
Further details of the results for individual regions are
given in Appendix~\ref{sec:notes-individual-hii}.

@@

The structure functions for the remaining Galactic sources
are shown in Figure~\ref{fig:strucfunc-fit-Galactic}b--d.
The data quality for these sources is not so high as for the inner Orion Nebula,
with the result that the model parameters are not so well constrained.
In particular, the relatively coarse spacing between nearest-neighbor spatial points
(see sections~\ref{sec:fabry-perot-etalaon} and \ref{sec:flames-multi-fiber})
means that the seeing has no effect on the observed structure function,
so that \(s_0\) is indeterminate in the model fits
(note the flat posterior histograms for \(s_0\) in Fig.~\ref{fig:corner-Galactic}c and d).
In addition, the effects of noise are also much greater,
as is apparent from visual inspection of the velocity fields
(top row of Figure~\ref{fig:velocity-maps}).
The principal effect of this on the model fits is to increase the uncertainty
in the power law slope \(m\).
The most extreme case is the Extended Orion Nebula (Fig.~\ref{fig:strucfunc-fit-Galactic}b),
where noise dominates the structure function at all scales.
The resultant degeneracy between parameters means that
is not possible to obtain a satisfactory fit
if all parameters are allowed to vary,
so we instead chose to fix the power slope at \(m = 1.0\),
which is close to the median value obtained for the other sources.

>>>>

\begin{figure*}
  \centering
  \sffigggg{OrionS}{OrionLH}{M8}{CarC}
  \caption{
    Second-order structure functions
    for velocity centroid images
    of the \ha{} emission line
    from Galactic \hii{} regions.
    The observed structure function \(B\obs(r)\) is shown by 
    blue symbols, with filled symbols indicating those points
    that are used to constrain the model fits.
    The full model is shown in orange,
    while the underlying ideal model
    (without the effects of seeing or noise)
    is shown in green.
    See text for details of the fitting process.
    (a)~Inner Orion Nebula.
    (b)~Extended Orion Nebula.
    (c)~M8, the Lagoon Nebula.
    (d)~Carina Nebula.
  }
  \label{fig:strucfunc-fit-Galactic}
\end{figure*}

@@

\begin{figure*}
  \centering
  \sffigg{Dor}{N346}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-Galactic}
    except for Magellanic Cloud \hii{} regions.
    (a)~30 Doradus in the LMC.
    (b)~NGC~346 in the SMC.    
  }
  \label{fig:strucfunc-fit-MC}
\end{figure*}

\begin{figure*}
  \centering
  \sffigggg{HV}{HX}{N595}{N604H}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-Galactic}
    except for \hii{} regions in more distant
    Local Group Galaxies.
    (a)~Hubble~V in NGC~6822.
    (b)~Hubble~X in NGC~6822.
    (c)~NGC~595 in M33.
    (d)~NGC~604 in M33.
  }
  \label{fig:strucfunc-fit-ExtraGal}
\end{figure*}

@@

In order to provide a uniform description of the velocity fluctuations,
we fit the model structure function
\(\tilde{B}\model(r)\) of equation~\eqref{eq:sf-functional}
to each \hii{} region in our sample.
Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
and~\ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
Best-fit values for the model parameters,
together with 95\% credibility range,
are given in Table~\ref{tab:Res}.
After describing the methods used to
measure the structure function and fit the model (section~\ref{sec:techn-deta-model}),
we give details of the results in the example case of
the inner Orion Nebula (\ref{sec:example-results-orion})
and a broad overview of the results for other regions (\ref{sec:results-model-fitt}).
Further details of the results for individual regions are
given in Appendix~\ref{sec:notes-individual-hii}.

@@

The structure functions for the remaining Galactic sources
are shown in Figure~\ref{fig:strucfunc-fit-Galactic}b--d.
The data quality for these sources is not so high as for the inner Orion Nebula,
with the result that the model parameters are not so well constrained.
In particular, the relatively coarse spacing between nearest-neighbor spatial points
(see sections~\ref{sec:fabry-perot-etalaon} and \ref{sec:flames-multi-fiber})
means that the seeing has no effect on the observed structure function,
so that \(s_0\) is indeterminate in the model fits
(note the flat posterior histograms for \(s_0\) in Fig.~\ref{fig:corner-Galactic}c and d).
In addition, the effects of noise are also much greater,
as is apparent from visual inspection of the velocity fields
(top row of Figure~\ref{fig:velocity-maps}).
The principal effect of this on the model fits is to increase the uncertainty
in the power law slope \(m\).
The most extreme case is the Extended Orion Nebula (Fig.~\ref{fig:strucfunc-fit-Galactic}b),
where noise makes a significant contribution to the structure function at all scales.
The resultant degeneracy between parameters means that
is not possible to obtain a satisfactory fit
if all parameters are allowed to vary,
so we instead chose to fix the power slope at \(m = 1.0\),
which is close to the median value obtained for the other sources.
